---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
## Load ggplot2
library(ggplot2)

## Load activity table, Transform the date into date syntax.
act = read.csv("activity.csv", sep = ",", header = TRUE, na.strings = "NA")
act$date = as.Date(act$date, format = "%m/%d/%Y")

```


## What is mean total number of steps taken per day?
- Calculate the mean and the median for total steps of each day:
```{r}
## Remove the missing values.
act = act[complete.cases(act), ]

## Split the table by the date, calculate sum of the steps for each days respectively.
spltAct = split(act, act$date)
ttStep = sapply(spltAct, function(x) return(sum(x$steps)))
meanttStep = mean(ttStep)
medianttStep = median(ttStep)
```

The mean of the total steps is `r meanttStep` steps.
The median of the total steps is `r medianttStep` steps.

- plot the histogram of the total steps count frequency:
```{r}

## Plot the histogram of the sum step for each day.
g = ggplot(act,aes(ttStep))
g + geom_histogram(binwidth = 700) + labs(title = "Total steps frequency count", x = "Steps taken in each day")

```

### Calculate the mean and the median for sum steps of each day:



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
